---
title: "Partial Comprehensive Report"
date: "June 18, 2018"
output:
  pdf_document:
    highlight: zenburn
    latex_engine: lualatex
  html_document: default
mainfont: Arial
params: 
  examinfo: NA
  infotable: NA 
  invalid_key: NA
  difficulty_indices: NA 
  psumm: NA
  phist: NA
  r_prime_values: NA
  r_primesumm: NA 
  r_prime_compare_values: NA 
  r_primehist: NA 
  r_primeless1: NA
  pnotbetween39: NA 
  nonfunctionaldistractors: NA 
  cron_alpha: NA 
  worst_5_questions: NA
  new_cron_alpha: NA 
  exceptional_questions: NA
---

# Information about your test

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
library(kableExtra)
kable(params$infotable, "latex", booktabs = TRUE) %>%
  kable_styling(position = "center")
```


```{r, echo = FALSE}
if (!is.null(params$invalid_key)) {
  sometext <- strsplit(params$invalid_key, " ")[[1]]
  text_formatted <- paste(
    text_spec(sometext, "latex", color = "red",
    font_size = 14),
    collapse = " ")
} else {
  text_formatted <- ""
}
```

`r text_formatted`

# Difficulty Indices

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
library(ggplot2)
kable(params$difficulty_indices, "latex", booktabs = TRUE) %>%
  kable_styling(position = "center")
kable(params$psumm, "latex", booktabs = TRUE) %>%
  kable_styling(position = "center")
params$phist
```

## Recommended Range for Difficulty Indices (<0.3 or >0.9)
 
Here are the questions on your test where the difficulty indices did NOT fall in the recommended range: 

```{r pnotbetween39, echo = FALSE, message = FALSE, warning = FALSE}
showtext <- FALSE
showtable <- FALSE
pnotbetween39printgood <- NULL
if (nrow(params$pnotbetween39) == 0) {
  pnotbetween39print <- "None of your questions had difficulty indices that fell outside of the recommended range! Great work."
  pnotbetween39printgood <- text_spec(pnotbetween39print, "latex", color = "#014421")
  showtext <- TRUE
} else {
 df <- params$pnotbetween39
 df <- df %>% 
        mutate(
          "Question" = cell_spec(Question, "latex", background = ifelse(hard == "Too Easy", "#9CE08B", "#E09C8B")),
          "p" = cell_spec(p, "latex", background = ifelse(hard == "Too Easy", "#9CE08B", "#E09C8B")),
          "hard" = cell_spec(hard, "latex", background = ifelse(hard == "Too Easy", "#9CE08B", "#E09C8B"))) %>%
        select(Question, p, hard)
      colnames(df) <- c("Question", "Difficulty Index", "This question was...")
      rownames(df) <- NULL

 pnotbetween39print <- kable(df, "latex", booktabs = TRUE, linesep = "", escape = FALSE) %>%
   kable_styling(position = "center")
 showtable <- TRUE
}
```

```{r, echo = FALSE, message = FALSE, warning = FALSE, results = "asis", eval = showtable}
pnotbetween39print
```

`r pnotbetween39printgood`

# Discrimination Coefficients 

```{r, echo = FALSE, message = FALSE, warning = FALSE}
kable(params$r_prime_values, "latex", booktabs = TRUE) %>%
  kable_styling(position = "center")
kable(params$r_primesumm, "latex", booktabs = TRUE) %>%
  kable_styling(position = "center")
params$r_primehist
```

## Flagged Questions Based on Discrimination Coefficients (< +0.10)

```{r rprimeless1, echo = FALSE, message = FALSE, warning = FALSE}
showtext <- FALSE
showtable <- FALSE
rprimeless1good <- NULL 
if (nrow(params$r_primeless1) != 0) {
  rprimeless1 <- kable(params$r_primeless1, "latex", booktabs = TRUE) %>%
    kable_styling(position = "center")
  showtable <- TRUE 
} else {
  rprimeless1 <- "None of the questions on your test had discrimination coefficients lower than +0.10. Great work!"
  rprimeless1good <- text_spec(rprimeless1, "latex", color = "#014421")
  showtext <- TRUE 
}
```

```{r, echo = FALSE, message = FALSE, warning = FALSE, results = "asis", eval = showtable}
rprimeless1
```

`r rprimeless1good` 

# Non-Functional Distractors (< 3% of students chose distractor)

Here is a list of questions on your test which had non-functional distractors: 

```{r nonfunctional, echo = FALSE, message = FALSE, warning = FALSE}
showtext <- FALSE
showtable <- FALSE
nonfunctionalgood <- NULL 
if (nrow(params$nonfunctionaldistractors) == 0) {
  nonfunctional <- "None of your questions had non-functional distractors. Great work!"
  nonfunctionalgood <- text_spec(nonfunctional, "latex", color = "#014421")
  showtext <- TRUE
} else {
  nonfunctional <- kable(params$nonfunctionaldistractors, "latex", booktabs = TRUE) %>%
    kable_styling(position = "center")
  showtable <- TRUE
}
```

```{r, echo = FALSE, message = FALSE, warning = FALSE, results = "asis", eval = showtable}
nonfunctional
```

`r nonfunctionalgood` 

# Reliability 

## Recommended Ranges for Reliability 

```{r, echo = FALSE, message = FALSE, warning = FALSE }
df <- data.frame("Reliability" = c("0.55 - 0.65", "0.65 - 0.8", "0.8 - 0.9", "0.9 - 1.0"), 
                 "Description" = c("Adequate for a midterm exam or term test/quiz", "Adequate for a final exam",
                                   "Excellent for a final exam or term test/quiz", "Standardized test level exam"))
rownames(df) <- NULL
kable(df, "latex", booktabs = TRUE) %>%
  kable_styling(position = "center")
```

The reliability of your test, currently, is `r params$cron_alpha`. 

```{r, echo = FALSE, message = FALSE, warning = FALSE}
shownewreliability <- FALSE
newreliabilitystring <- NULL
newreliabilitystring2 <- NULL
if (params$new_cron_alpha > params$cron_alpha) {
  shownewreliability <- TRUE
} 
```

```{r, echo = FALSE, message = FALSE, warning = FALSE, eval = shownewreliability}
newreliabilitystring <- "Often, removing questions with low discrimination coefficients from your test can greatly improve the reliability of your test. Here are the 5 questions on your test with the lowest discrimination coefficients:"
```

`r newreliabilitystring`

```{r, echo = FALSE, message = FALSE, warning = FALSE, eval = shownewreliability}
kable(params$worst_5_questions, "latex", booktabs = TRUE) %>%
  kable_styling(position = "center")
newreliabilitystring2 <- paste("If you were to simply remove these 5 questions from your test altogether, the reliability of your test would have been ", params$new_cron_alpha, ".", sep = "")
```

`r newreliabilitystring2` 

# Exceptional Questions (Discrimination Coefficient +0.40 or higher)

```{r, echo = FALSE, message = FALSE, warning = FALSE}
showtext <- FALSE
showtable <- FALSE
exceptionalbad <- NULL 
if (nrow(params$exceptional_questions) == 0) {
  exceptional <- "Unfortunately, none of your questions had a discrimination coefficient of +0.40 or higher. Try rewording some of your questions in future iterations of your test, and hopefully you will be able to meet this threshold eventually. Don't feel bad -- this is an extremely difficult threshold to reach!"
  exceptionalbad <- text_spec(exceptionalbad, "latex", color = "red")
  showtext <- TRUE
  exceptional
} else {
  exceptional <- kable(params$exceptional_questions, "latex", booktabs = TRUE) %>%
    kable_styling(position = "center")
  showtable <- TRUE
}
```

`r exceptionalbad`

```{r, echo = FALSE, message = FALSE, warning = FALSE, results = "asis", eval = showtable}
exceptional
```